---
title: "Lab 5"
output: html_document
---
```{r, load}
library(tidyverse)
lotr  <- read_csv("https://raw.githubusercontent.com/jennybc/lotr-tidy/master/data/lotr_tidy.csv") %>% 
  rename(Species = Race)
```

Would you say this data is in tidy format?
##Yes because each film has individual data for the count of words. 


Widen the data so that we see the words spoken by each species, by putting species as its own column.
```{r, wide}
lotr_wide <- lotr %>%
  pivot_wider(id_cols = c(-Species, -Words), 
              names_from = Species, 
              values_from = Words)
```


Re-lengthen the wide LOTR data from Question 2 above.
```{r,  }
lotr_wide %>%
  pivot_longer(cols = Elf:Man, 
               names_to  = "Species", ##these need to be in quotes because there is no column or data named species
               values_to = "Words")
```

```{r}
library(tidyverse)
set.seed(123)
missing_w2_parent <- sample(1:500, 30)
missing_w2_child <- c(missing_w2_parent[1:5], sample(1:500, 25))
family  <- read_csv(
  "https://raw.githubusercontent.com/bwiernik/progdata/main/inst/tutorials/data/family_data.csv"
) %>% 
  mutate(
    across(
      starts_with("w2") & contains("parent"),
      ~ ifelse(family_id %in% missing_w2_parent, NA_real_, .x)
    ),
    across(
      starts_with("w2") & contains("child"),
      ~ ifelse(family_id %in% missing_w2_child, NA_real_, .x)
    )
  )
```

You’re working on a longitudinal study of parent-child relationships. You have collected data from 500 families over 2 waves. In each wave, both the child and parent completed measures of communication behavior and relationship satisfaction.

```{r}
family %>% 
  DT::datatable(rownames = FALSE)
```

Reshape the dataset to a “longer” format.
Make each row 1 score
Have columns for family_id, family_member, wave, scale, and score.

```{r}
family_longest <- family %>% 
  pivot_longer(
    cols = -family_id,
    names_to = c("wave", "scale", "family_member"), 
    names_sep = "_",
    values_to = "score"
  )

print(family_longest)
```

Reshape the dataset to a “longer” format.
Make each row 1 person
Have columns for family_id, family_member, wave, comm, and satis.

```{r}
family_long <- family %>%
  pivot_longer(
    cols = -family_id,
    names_to = c("wave", ".value", "family_member"), 
    names_sep = "_"
  )

print(family_long)
```

Some families are missing wave 2 data for parent, child, or both. Which families are missing wave 2 data for at least one person?
Question: Is is easier to easier to find the missing data in the wide or long format?
##I think it is easier to see missing values in the wide format since there are less rows and overal better way to visulaize the data in terms of first glance. 
