---
title: "Lab 6"
output: html_document
---

```{r}
library(tidyverse)
```

34.1 Exercise 1: singer
The package singer comes with two smallish data frames about songs. Let’s take a look at them (after minor modifications by renaming and shuffling):

You can download the singer data from the class repo:
```{r}
songs <- read_csv("https://raw.githubusercontent.com/bwiernik/progdata-class/master/data/singer/songs.csv")
locations <- read_csv("https://raw.githubusercontent.com/bwiernik/progdata-class/master/data/singer/loc.csv")

(time <- as_tibble(songs) %>%
   rename(song = title))

(album <- as_tibble(locations) %>% 
   select(title, everything()) %>% 
   rename(album = release,
          song  = title))
```

We really care about the songs in time. But, for which of those songs do we know its corresponding album?
```{r}
time %>% 
  left_join(
    album, 
    by = c("song", "artist_name")
    )
```


Which songs do we have “year”, but not album info?
```{r}
time_2 <- time_1 %>% 
  anti_join(album, by = "song")
```
##Corduroy, Martin_Doom!It's Seven O'Clock, Leaves And Sand, Comb Your Hair, Mine Again, Don't Forget About Us, Babydoll, and Vision of Love.


Which artists are in time, but not in album?
```{r}
time %>% 
  anti_join(album, by = "artist_name")
```
##Mariah Carey

You’ve come across these two tibbles, and just wish all the info was available in one tibble. What would you do?
```{r}
album_time <- album %>% 
  left_join(time, by = "song")
```


34.2 Exercise 2: LOTR
Load in three tibbles of data on the Lord of the Rings:
```{r}
fell <- read_csv("https://raw.githubusercontent.com/jennybc/lotr-tidy/master/data/The_Fellowship_Of_The_Ring.csv")
ttow <- read_csv("https://raw.githubusercontent.com/jennybc/lotr-tidy/master/data/The_Two_Towers.csv")
retk <- read_csv("https://raw.githubusercontent.com/jennybc/lotr-tidy/master/data/The_Return_Of_The_King.csv")
```

```{r}
glimpse(fell)
glimpse(ttow)
glimpse(retk)
```

Stack these into a single tibble.
```{r, 2Q1}
bind_rows(
  fell, ttow
)
bind_cols(
  fell, ttow
)
```
## 2. Which races are present in “The Fellowship of the Ring” (fell), but not in any of the other ones?
```{r, 2Q2}
fell %>% 
  anti_join(ttow, by = "Race") %>% 
  anti_join(retk, by = "Race")
```



