---
title: "Lab 4"
author: "Jason R. Schmidt Avendano"
date: !r format(Sys.Date())
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, load}
library(tidyverse)
```

```{r, Data}
dat_gdata <- read_csv(here::here("Data", "green_data.csv"))
dat_gdic <- read_csv(here::here("Data", "green_dictionary.csv"))
```

Inspect the item responses (e.g., with graphs or by summarizing distinct values). Is anything unusual?

```{r, Q1a}
dat_gdata %>% 
  glimpse()

dat_gdic %>% 
  glimpse()
```

```{r, Q1b}
dat_gdata %>% 
  select(-id) %>% 
  unlist() %>% 
  unique() ##This allows us to look only at the response values since we took id out, and see which values are unique

```

```{r, Q1c}
dat_gdata %>% 
  mutate(
    across(
      -id, 
      function(x) recode(x, "1" = 1, "2" = 2, "3" = 3, "4" = 4, "5" = 5, "-99" = NA_real_)
    )
  )

```

```{r, Q1d}
dat_gdata <- dat_gdata %>% 
  mutate(
    across(
      -id, 
      function(x) na_if(x, -99)
    )
  )
```

Compute total scores for the four scales. Recode variables as needed.

```{r, Q2a}
reversed <- dat_gdic %>% 
  filter(Keying == -1) %>% 
  pull(Item) ##This just puts it in a vector, so a list of all the items. If you want this to be in a table 
```


```{r, Q2b}

reverse_item <- function(x) (
  recode(x, "1" = 5, "2" = 4, "3" = 3, "4" = 2, "5" = 1)
)

dat_gdata <- dat_gdata %>% 
  mutate(
    across(
      all_of(reversed),
      reverse_item
    )
  )

##This was the long way, above is the efficient way to do it across all columns

# dat_gdata %>%
#   mutate(
#     green2 = recode(green2, "1" = 5, "2" = 4, "3" = 3, "4" = 2, "5" = 1),
#     comp6 = recode(comp6, "1" = 5, "2" = 4, "3" = 3, "4" = 2, "5" = 1),
#     comp7 = recode(comp7, "1" = 5, "2" = 4, "3" = 3, "4" = 2, "5" = 1),
#     comp8 = recode(comp8, "1" = 5, "2" = 4, "3" = 3, "4" = 2, "5" = 1),
#     comp9 = recode(comp9, "1" = 5, "2" = 4, "3" = 3, "4" = 2, "5" = 1),
#     comp10 = recode(comp10, "1" = 5, "2" = 4, "3" = 3, "4" = 2, "5" = 1), 
#     intel7 = 6 - intel7, 
#     intel8 = 6 - intel8, 
#     intel9 = 6 - intel9, 
#     intel10 = 6 - intel10, 
#     open7 = 6 - open7, 
#     open8 = 6 - open8, 
#     open9 = 6 - open9, 
#     open10 = 6 - open10
#     )
```

```{r, Q2c}
dat_gdata <- dat_gdata %>%
  rowwise() %>% 
  mutate(
    id = id,
    green_total = mean(c_across(green1:green5), na.rm = TRUE),
    comp_total = mean(c_across(comp1:comp10), na.rm = TRUE),
    intel_total = mean(c_across(intel1:intel10), na.rm = TRUE),
    open_total = mean(c_across(open1:open10), na.rm = TRUE),
    .before = everything()
  )

ggplot(data = dat_gdata,
       mapping = aes(x = green_total)) +
  geom_histogram()

print(dat_gdata)
```

Rescale the variables so that they go from 0-100 instead of the original range. Name the recaled variables *_pomp.
```{r, Rescale}
dat_gdata <- dat_gdata %>% 
  mutate(
    across(
      green_total:open_total, 
      function(x) datawizard::change_scale(x, range(1,5), to = c(0, 100)), 
      .names = "{.col}_pomp"
    ), 
    .after = open_total
  )

print(dat_gdata)
```


Make plots that illustrate the distributions of the 4 POMP-scored variables.
```{r, Plots}
ggplot(data = dat_gdata,
       mapping = aes(x = green_total_pomp)) +
  geom_histogram()

ggplot(data = dat_gdata,
       mapping = aes(x = comp_total_pomp)) +
  geom_histogram()

ggplot(data = dat_gdata,
       mapping = aes(x = intel_total_pomp)) +
  geom_histogram()

ggplot(data = dat_gdata,
       mapping = aes(x = open_total_pomp)) +
  geom_histogram()
```


Make scatterplots showing the relationships between green reputation and each personality trait. Include trend lines for students and non-students. What do these plots show?
```{r, Scatterplots}
dat_gdata %>%
  drop_na(student) %>%
ggplot() + 
    aes(x = open_total_pomp, y = green_total_pomp, color = factor(student)) +
  geom_point() + 
  geom_smooth(method = lm)
```


Compare green reputation for students and non-students using a rainfall plot (bar + density + data points).
```{r, Compare}

```


Compute a summary table of means, SDs, medians, minima, and maxima for the four total scores for students and non-students.
```{r, Compute}

```

