---
title: "Lab 4"
author: "Jason R. Schmidt Avendano"
date: !r format(Sys.Date())
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, load}
library(tidyverse)
```

```{r, Data}
dat_gdata <- read_csv(here::here("Data", "green_data.csv"))
dat_gdic <- read_csv(here::here("Data", "green_dictionary.csv"))
```

```{r, Glimpse}
dat_gdata %>% 
  glimpse()

dat_gdic %>% 
  glimpse()
```


Inspect the item responses (e.g., with graphs or by summarizing distinct values). Is anything unusual?

```{r, Recode}
dat_gdata %>%
  mutate(
    green2 = recode(green2, "1" = 5, "2" = 4, "3" = 3, "4" = 2, "5" = 1),
    comp6 = recode(comp6, "1" = 5, "2" = 4, "3" = 3, "4" = 2, "5" = 1),
    comp7 = recode(comp7, "1" = 5, "2" = 4, "3" = 3, "4" = 2, "5" = 1),
    comp8 = recode(comp8, "1" = 5, "2" = 4, "3" = 3, "4" = 2, "5" = 1),
    comp9 = recode(comp9, "1" = 5, "2" = 4, "3" = 3, "4" = 2, "5" = 1),
    comp10 = recode(comp10, "1" = 5, "2" = 4, "3" = 3, "4" = 2, "5" = 1), 
    intel7 = 6 - intel7, 
    intel7 = 6 - intel7, 
    intel7 = 6 - intel7, 
    intel7 = 6 - intel7, 
    intel7 = 6 - intel7, 
    intel7 = 6 - intel7, 
    )
```


```{r, Inspect}
dat_gdata %>%
  rowwise() %>% 
  mutate(
    id = id,
    green_total = mean(c_across(green1:green5), na.rm = TRUE),
    comp_total = mean(c_across(comp1:comp5), na.rm = TRUE),
    intel_total = mean(c_across(intel1:intel5), na.rm = TRUE),
    open_total = mean(c_across(open1:open5), na.rm = TRUE),
    .before = everything()
  )

ggplot(data = dat_gdata,
       mapping = aes(x = green_total)) +
  geom_histogram()

print(dat_gdata)
```


Compute total scores for the four scales. Recode variables as needed.
```{r, Total Scores}

```


Rescale the variables so that they go from 0-100 instead of the original range. Name the recaled variables *_pomp.
```{r, Rescale}

```


Make plots that illustrate the distributions of the 4 POMP-scored variables.
```{r, Plots}

```


Make scatterplots showing the relationships between green reputation and each personality trait. Include trend lines for students and non-students. What do these plots show?
```{r, Scatterplots}

```


Compare green reputation for students and non-students using a rainfall plot (bar + density + data points).
```{r, Compare}

```


Compute a summary table of means, SDs, medians, minima, and maxima for the four total scores for students and non-students.
```{r, Compute}

```

