---
title: "Lab 02 - Plastic waste"
author: "Jason R. Schmidt Avendano"
date: !r format(Sys.Date())
output: html_document
---

## Load packages and data

```{r setup, message=FALSE}
library(tidyverse)
```

```{r load-data, message=FALSE}
plastic_waste <- read.csv(here::here("Data", "plastic_waste.csv"))
```

## Exercises

### Exercise 1

Africa & Asia seem to have the most plastic waste per capita, followed by a moderate amount in Europe & North America, with the least in Oceania & South America. This visualization is not very clear. 

```{r plastic-waste-continent}
ggplot(plastic_waste) + 
  aes(x = plastic_waste_per_cap) + 
  geom_histogram() + 
  facet_wrap(~continent)
```





### Exercise 2

```{r plastic-waste-density}
ggplot(plastic_waste) + 
  aes(x = plastic_waste_per_cap) + 
  geom_density(aes(y = after_stat(count))) + 
  facet_wrap(~continent)
```

```{r, density plot colored}
ggplot(plastic_waste) + 
  aes(x = plastic_waste_per_cap, color = continent) + 
  geom_density(aes(y = after_stat(count))) 
```

```{r}
ggplot(plastic_waste) + 
  aes(x = plastic_waste_per_cap, color = continent, fill = continent) + 
  geom_density(aes(y = after_stat(count))) 
```

```{r}
ggplot(plastic_waste) + 
  aes(x = plastic_waste_per_cap, color = continent, fill = continent) + 
  geom_density(alpha = .25) 
```


### Exercise 3

Fill and color go in aes because the is a global change, that causes the variables to be mapped on all variables in graph. For alpha we only want it to effect the density portion of our graph.

### Exercise 4

Remove this text, and add your answer for Exercise 4 here.

```{r plastic-waste-violin}
# insert code here
```

### Exercise 5

Remove this text, and add your answer for Exercise 5 here.

```{r plastic-waste-mismanaged}
# insert code here
```

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.

```{r plastic-waste-mismanaged-continent}
# insert code here
```

### Exercise 7

Remove this text, and add your answer for Exercise 7 here.

```{r plastic-waste-population-total}
# insert code here
```

```{r plastic-waste-population-coastal}
# insert code here
```

### Exercise 8

Remove this text, and add your answer for Exercise 8 here.

```{r recreate-viz}
# insert code here
```

## Pro-Tips

### Excercise 3

Try this :D

```
ggplot(data = plastic_waste, 
       mapping = aes(x = continent, 
                     y = plastic_waste_per_cap)) +
  geom_violin()+
  geom_boxplot(width=.3, fill="green") +
  stat_summary(fun.y=median, geom="point") 
```

### Exercise 5 

Helpful reference:http://www.sthda.com/english/wiki/ggplot2-themes-and-background-colors-the-3-elements



