---
title: "ggplot"
output: html_document
---

```{r, Setup}
library(easystats)
library(tidyverse)
library(gapminder)
```

```{r, Data}
gapminder
plot(airquality)
##plot allows us to simply visualize the data 
```


#data
  This is the data that you are feeding into the plot 
#aesthetic mapping 
  How are variables in the data connecting to a visual dimension
      x and y positioning, color fill, shape, line type, size, transperancy, etc. 
#Geometric objects
  What are the objects actually drawn on the plot? 
      points, bars, lines, density, etc. 
#Scales
  How is a varaible mapped to its asethtic? 
      Is it linear, log scale, etc.? 
#Stats transformations 
  How the data are combined/transformed before plotting 
      Bar chart = data transformed into frequencies 
#Facet
  Breaking up the data in to panels, "sub plots" 
  
```{r, Grammar of Graphics Example #1}
ggplot(gapminder)
```

```{r empty graph}
ggplot(gapminder) +
  aes(x = gdpPercap, y = lifeExp)
```

```{r, coordinates}
ggplot(gapminder) +
  aes(x = gdpPercap, y = lifeExp) + 
  geom_point()
```

```{r, color}
ggplot(gapminder) +
  aes(x = gdpPercap, y = lifeExp) + 
  geom_point(color = "dark orange")
```

```{r, alpha}
ggplot(gapminder) +
  aes(x = gdpPercap, y = lifeExp) + 
  geom_point(color = "dark orange", alpha = .15)
```

```{r, scale}
ggplot(gapminder) +
  aes(x = gdpPercap, y = lifeExp) + 
  geom_point(color = "dark orange", alpha = .15) + 
  scale_x_continuous(
    name = "GDP per capita", 
    trans = "log10", 
    labels = scales::dollar_format()
  )
```

